---
title: "FARS Functionality"
author: "Manuel Odendahl"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
devtools::load_all()
```

This package provides functionality to interact with the \href{Fatality Analysis Reporting System}{https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars} database.
Given a set of `.csv.gz` datafiles, summaries about the number of accidents per year

## Input data

The FARS package needs data files for each year.
The files need to be provided in the working directory and named `accident_YEAR.csv.bz2`.
They can be read using the `fars_read_years` function, which returns a list of accidents counts by month and year.

```{r}
dir(getwd())
fars_read_years(2013)
```

## Summarizing yearly reports

You can get a report about years by using the function `fars_summarize_years`.

```{r}
fars_summarize_years(2013)
```

## Map plots

Finally, you get a plot of all the accidents in a state using the `fars_map_state` function.

```{r, echo=FALSE, results='asis'}
fars_map_state(4, 2013)
```

